---
title: "KmeansUsage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{KmeansUsage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# K-Means Clustering Package

This vignette demonstrates the functionality of the `Kmeans` package, including clustering, visualization, and performance benchmarking.

## Installation

To install the package from GitHub:

```{r}
devtools::install_github("Cameron-zgl/625_mypackage")
```

## Example Usage

### Clustering with `my_kmeans`

```{r}
library(Kmeans)

# Example data
data <- matrix(rnorm(1000), ncol = 2)

# Clustering
result <- my_kmeans(data, centers = 3, nstart = 10)
print(result)

```

Visualization of Clusters

```{r}
# Visualizing the clustering result
plot_clusters(data, result$cluster, result$centers)

```

### Performance Benchmarking

Here we compare the performance of `my_kmeans` and base R's `kmeans` function.

```{r}
# Benchmarking
benchmark <- benchmark_kmeans(data, centers = 3, nstart = 10)
print(benchmark)

```

The benchmark results show the following:

-   **Base R `kmeans` function**: Typically faster but uses fixed methods.

-   **`my_kmeans` function**: Includes enhancements like better modularity, and integration with this package's visualization.

```{r}
# Display the benchmark result
benchmark

```
